Report on the Third Workshop on Sustainable Software for Science: Practice and Experiences (WSSSPE3)

### 2015-12-03 WSSSPE3/report/wg_main_training.tex
Update wg_main_training.tex
- added \cite refs

\item Workshop on Sustainable Software for Science: Practice and
Experiences (WSSSPE)\footnote{\url{http://wssspe.researchcomputing.org.uk/}}
\katznote{change to cite}

\item International Workshop on Software Engineering for High
Performance Computing in Computational Science and
Engineering (SEHPCCSE)\footnote{\url{http://wssspe.researchcomputing.org.uk/}}
\katznote{fix URL and change to cite}

\item Workshop on Software Engineering for Sustainable Systems\footnote{\url{http://sustainabilitydesign.org/initiatives/se4susy/}}
\katznote{fix URL and change to cite}

>>>>

\item Workshop on Sustainable Software for Science: Practice and
Experiences (WSSSPE)~\cite{WSSSPE}

\item International Workshop on Software Engineering for High
Performance Computing in Computational Science and
Engineering (SEHPCCSE)~\cite{SEHPCCSE}

\item Workshop on Software Engineering for Sustainable Systems~\cite{se4susy}
